Age-related changes in plant growth and traits

### 2015-08-06 Panalysis.rmd
new file on details of errors to fix - same info as in "issues" I've posted
new file that is follow up on today's conversation with Mark and needs to be intregrated into other files

continued bits of other work, mostly trying to tidy up accessory tissue thoughts

check <- PEPU_Investment
check_FD <-check[3]
View(check_FD)
check3 <- subset(check_FD,FD.what=="cone_aborted")

names(check_FD)

>>>>

check_FD <-as.data.frame(PEPU_Investment[3])
check_FD_aborted <- subset(check_FD,FD.what=="cone_aborted")
check_FD_aborted

check_parts <- subset(as.data.frame(PEPU_FlowerPartsData),what=="cone_aborted")
check_parts <- subset(as.data.frame(PEPU_FlowerPartsData),part=="cone_aborted")
check_parts

names(check_parts)
